---
title: "working_doc"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Working Doc

Here is where is where I will have working notes and preliminary code. 

Think of this as a notepad -- it's not really meant for outside eyes as it's just a place for me to get my thoughts and dirty code down. Read on if you dare.  

As the project progresses, I will move the working code into dedicated scripts and delete the working notes (ex: planning, to-do's and resources) that have been implemented.  

```{r}
library(tidyverse)
library(plyr)

mental_health <- read_csv("../data/mental_health.csv")

glimpse(mental_health)

# Vector of Provinces to keep
provinces <- mental_health$GEO %>% factor() %>% levels()
provinces <- provinces[!provinces %in% c("Canada", "Atlantic Provinces", "Prairie Provinces")]

# Vector of Ages to keep
ages <- mental_health$AGE %>% factor() %>% levels()
ages <- ages[c(1,2,4,5, 6)]
ages_clean <- c("Total", "15 to 24", "25 to 44", "45 to 64", "65 +")

stress_level <- c("Self-rated work stress, days not at all or not very stressful", "Self-rated work stress, days quite a bit or extremely stressful")
stress_level_clean <- c("Low Stress", "High Stress")

perceived_need <- c("Perceived need for mental health care, need not met", 
                    "Perceived need for mental health care, all needs met")
perceived_need_clean <- c("Needs not Met", "Needs Met")


perceived_mental_health <- c("Perceived mental health, fair or poor", "Perceived mental health, very good or excellent")
perceived_mental_health_clean <- c("Poor Mental Health", "Good Mental Health")


general_disorders <- c("Any mood disorder, life", "Major depressive episode, life" , 
               "Bipolar disorder, life", "Generalized anxiety disorder, life",
               "Suicidal thoughts, life", "Schizophrenia or psychosis, ever received diagnosis", "Post-traumatic stress disorder, current diagnosed condition")

general_disorders_clean <- c("Any Disorder", "Depression", "Bipolar", "Anxiety", "Suicidal", "Psychosis", "PTSD")
               
substance_disorders  <- c("Any substance use disorder (alcohol or drug), life", 
                          "Alcohol abuse or dependence, life" ,
                          "Cannabis abuse or dependence, life", 
                          "Other drug abuse or dependence (excluding cannabis), life")
substance_disorders_clean <- c("Any Substance", "Alcohol", "Cannabis", "Other")


(mental_health_reduced <- mental_health %>% 
  # Filter to only have Number of Persons and Percent, and only from year 2012
  filter(UNIT %in% c("Number of persons","Percent"), Ref_Date == 2012) %>% 
  # Filter to only have provinces 
  filter(GEO %in% provinces) %>% 
  # Filter to only have unique ages (no overlap ranges)
  filter(AGE %in% ages) %>% 
  # Change Units
  mutate(Value = as.double(Value)) %>% 
  # Select only variables that are actually being used later
  dplyr::select(-c(Ref_Date, Vector, Coordinate)) %>% 
  
  # Filter HRPROF (i.e. variables) by category
  filter(HRPROF %in% stress_level |
           HRPROF %in% perceived_need |
           HRPROF %in% perceived_mental_health |
           HRPROF %in% general_disorders |
           HRPROF %in% substance_disorders) %>% 
  
  # Change Variables so cleaner names
  mutate(HRPROF = mapvalues(HRPROF, stress_level, stress_level_clean)) %>% 
  mutate(HRPROF = mapvalues(HRPROF, perceived_need, perceived_need_clean)) %>% 
  mutate(HRPROF = mapvalues(HRPROF, perceived_mental_health, perceived_mental_health_clean)) %>% 
  mutate(HRPROF = mapvalues(HRPROF, general_disorders, general_disorders_clean)) %>% 
  mutate(HRPROF = mapvalues(HRPROF, substance_disorders, substance_disorders_clean)) %>% 
  mutate(SEX = mapvalues(SEX, c("Both sexes"), c("Both"))) %>% 
  mutate(UNIT = mapvalues(UNIT, c("Number of persons"), c("Number"))) %>% 
  mutate(AGE = mapvalues(AGE, ages, ages_clean)) %>% 
    
  
  # Mutate values that are percent so that can be rendered effectively later  
  mutate(Value = ifelse(UNIT == "Percent", Value/100, Value))
  
  )


age_input

ages
ages_clean

## FUTURE Buttons

age_input  <- mental_health_reduced$AGE %>% unique()
provinces_input <- provinces
sex_input <- mental_health_reduced$SEX %>% unique()
unit_input <- mental_health_reduced$UNIT %>% unique()

stress_level_clean <- c("Low Stress", "High Stress")
perceived_need_clean <- c("Needs not Met", "Needs Met")
perceived_mental_health_clean <- c("Poor Mental Health", "Good Mental Health")

perceptions_input <- list(stress_level_clean, perceived_need_clean, perceived_mental_health_clean)


substance_disorders_clean <- c("Any Substance", "Alcohol", "Cannabis", "Other")
general_disorders_clean <- c("Any Disorder", "Depression", "Bipolar", "Anxiety", "Suicidal", "Psychosis", "PTSD")

disorders_input <- list(general_disorders_clean, substance_disorders_clean)

mental_health_reduced

```



```{r}

# Perceived Mental Health State
mental_health_reduced %>% 
  filter(HRPROF %in% grep("Perceived mental", HRPROF,  value = TRUE)) %>% 
  separate(col = HRPROF, into = c("Perceived mental health", "level"), sep = ", ")

# Perceived Mental Health GOOD
mental_health_reduced %>% 
  filter(HRPROF == "Perceived mental health, good" |
           HRPROF == "Perceived mental health, very good or excellent") %>% 
  group_by(GEO, AGE, SEX) %>% 
  mutate(n_persons = mean(`Number of persons`))

# Grepping multiple patterns - https://stackoverflow.com/questions/7597559/grep-using-a-character-vector-with-multiple-patterns

```



Ideas:
- Render all of Canada shaded in different colours, checking either 1) Perceived Mental Health 2) Perceived Need for Mental Health 3) Self-Rated Stress
- Within each Province Click - 
  - Input Controls: 1) Gender 2) Age Included 3) Percentage vs. Count
  - Render - Percentage Suicidal (as NUMBER)
  - Render - Percentage Mental Health Services Accessed
  - Render - Mood Disorders bar chart (maybe include others -- PTSD, Schizophrenia?)  
  - Render - Substance Use bar Chart
- For all can toggle PERCENTAGE vs. COUNT



## From Class + Tutorials 

Tutorial from 545: http://stat545.com/shiny00_index.html


Go through the tutorials: https://shiny.rstudio.com/tutorial/  

note: reactive vs. eventreactive -- if want to it update on click of a button do eventreactive

in server.R -- can use renderUI to automatically generate checkboxes (her example, giving all the country names)

plotOutput -- use the click argument or hover, etc. 



Use this for colouring of Maps: http://colorbrewer2.org/#type=sequential&scheme=OrRd&n=4  

## ggmaps:

http://rforpublichealth.blogspot.ca/2015/10/mapping-with-ggplot-create-nice.html:

http://unconj.ca/blog/choropleth-maps-with-r-and-ggplot2.html  


## Leaflets Tutorial: 

https://www.r-bloggers.com/4-tricks-for-working-with-r-leaflet-and-shiny
---- "Code | Trick2 | Graph depends on click"  --  this will be really useful for SAVING what's highlighted as a reactive varaible for use in a graph


Highlight Options -- https://rstudio.github.io/leaflet/shapes.html  (Can highlight a Province)  --- this is from hover, need to modify it so that it's on click.

https://www.r-graph-gallery.com/183-choropleth-map-with-leaflet/  

GREAT link for having reactive plots based on click of polygon: https://stackoverflow.com/questions/33575321/how-to-create-an-event-when-pressing-on-a-leaflet-popup-in-r

## Shiny Dashboard

https://rstudio.github.io/shinydashboard/get_started.html

Look at example: https://github.com/rstudio/shiny-examples/tree/master/086-bus-dashboard


## Playing around with leaflet
```{r}

library(rgeos)
library(raster)

canada <- getData('GADM', country = "CAN", level = 1)
#%>% gSimplify(0.001)
#subset <- c("Alberta", "British Columbia", "Manitoba", "New Brunswick", "Newfoundland and Labrador", "Nova Scotia", "Ontario", "Prince Edward Island", "Québec", "Saskatchewan")

#canada <- subset(canada, NAME_1 %in% subset)


#getSmallPolys <- function(poly, minarea=0.01) {
  # Get the areas
  areas <- lapply(poly@polygons, 
                  function(x) sapply(x@Polygons, function(y) y@area))

  # Quick summary of the areas
  print(quantile(unlist(areas)))

  # Which are the big polygons?
  bigpolys <- lapply(areas, function(x) which(x > minarea))
  length(unlist(bigpolys))

  # Get only the big polygons and extract them
  for(i in 1:length(bigpolys)){
    if(length(bigpolys[[i]]) >= 1 && bigpolys[[i]] >= 1){
      poly@polygons[[i]]@Polygons <- poly@polygons[[i]]@Polygons[bigpolys[[i]]]
      poly@polygons[[i]]@plotOrder <- 1:length(poly@polygons[[i]]@Polygons)
    }
  }
  return(poly)
#}

#canada <- getSmallPolys(canada)

leaflet() %>% addTiles() %>% addPolygons(data = canada, weight = 2)
```


```{r}
library(rgeos)
library(maptools)
library(ggmap)
library(rgdal)

# Download Boundary files by: http://www12.statcan.gc.ca/census-recensement/2011/geo/bound-limit/bound-limit-2011-eng.cfm  
getwd()
canada_poly <- readOGR(dsn = ".", layer = "gpr_000a11a_e")

subset <- c("Alberta", "British Columbia", "Manitoba", "New Brunswick", "Newfoundland and Labrador", "Nova Scotia", "Ontario", "Prince Edward Island", "Quebec", "Saskatchewan")


canada_poly <- subset(canada_poly, PRENAME %in% subset)
canada$PRENAME
(mh_df<- mental_health_reduced %>% 
  mutate(PRENAME = GEO) %>% 
  dplyr::select(-GEO) %>% 
         filter(HRPROF == "Suicidal") %>% 
         filter(UNIT == unit_input[2]) %>% 
         filter(AGE == age_input[4]) %>% 
        filter(SEX == "Both"))
mh_df <- mh_df %>% as.data.frame()

row.names(mh_df)

canada_df <- canada_poly %>% as.data.frame()

canada_df <- canada_df %>% mutate(PRUID = revalue(PRUID, c("48" = "Alberta", 
                                           "24" = "Quebec",
                                           "12" = "Nova Scotia",
                                           "13" = "New Brunswick", 
                                           "46" = "Manitoba", 
                                           "59" = "British Columbia", 
                                           "11" = "Prince Edward Island",
                                           "10" = "Newfoundland and Labrador",
                                           "47" = "Saskatchewan",
                                           "35" = "Ontario")))

canada_complete <- SpatialPolygonsDataFrame(Sr = canada_poly, data = canada_df)
                                           
canada %>% dplyr::select(PRUID, PRENAME)

getSpPPolygonsIDSlots(canada_complete)

spdf_canada <- SpatialPolygonsDataFrame(Sr = canada_complete, data = mh_df)

maybe <- merge(canada_complete, mh_df, by.x = "PRUID", by.y = "PRENAME")

maybe@data

canada_fort <- fortify(canada)

test_pieces <- c(1:12)

canada_fort <- canada_fort %>% filter(id %in% test_pieces)

pal <- colorQuantile("YlOrRd", maybe$Value) maybe$Value

leaflet() %>% addTiles() %>% addPolygons(data = maybe, color = "#444444", weight = 1, smoothFactor = 0.5,
    opacity = 1.0, fillOpacity = 0.5,
    fillColor = ~pal,
    highlightOptions = highlightOptions(color = "white", weight = 2,
      bringToFront = TRUE)) %>% addLegend(position = "bottomright",pal = colorQuantile("YlOrRd", maybe$Value), value = maybe$Value)



```

## Just do it in ggmap and be done with it.. 

http://rforpublichealth.blogspot.ca/2015/10/mapping-with-ggplot-create-nice.html  




```{r}

ggplot(mental_health_reduced %>% 
         filter(HRPROF %in% disorders_input[[1]]) %>% 
         filter(GEO == provinces_input[2]) %>% 
         filter(UNIT == unit_input[2]) %>% 
         filter(AGE == age_input[4])) +
  geom_bar(aes(x = HRPROF, y = Value), stat = "identity", 
           fill = "light blue",
           colour = "light blue") +
  labs(y = "Percent", 
       title = paste("Province:", provinces_input[2], "\n", "Age:", age_input[4]), 
       x = "Mental Health Disorders") +
  scale_fill_discrete(drop = FALSE) +
  scale_x_discrete(drop = FALSE) +
  scale_y_continuous(labels = scales::percent_format()) +
  theme_minimal()
  
  
mental_health_reduced %>% 
         filter(HRPROF == "Suicidal") %>% 
         filter(GEO == provinces_input[2]) %>% 
         filter(UNIT == unit_input[2]) %>% 
         filter(AGE == age_input[4]) %>% 
        filter(SEX == "Both") %>% 
  .$Value %>% scales::percent()
```



